---
title       : What Characteristics of Red Wine determine its quality?
subtitle    : Exploratory Data Analysis of Red Wine Data
author      : Steven Wang
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [bootstrap]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Introduction

This app serves for Red Wine Quality data exploratory analysis.

The red wine data set can get from [Machine Learning Repository website](https://archive.ics.uci.edu/ml/datasets/Wine+Quality), which was donated by Paulo Cortez, University of Minho, Portugal. This data set has 1599 obervations and 12 variables

A new variable class was added into the data set while performing this analysis. The class is a categorical variable and is defined by this rules:

* if quality <= 4, then "Low Quality"
* if quality >= 7, then "High Quality"
* else "Average"

--- .class #id 

## A peek of Red Wine Data Set

```{r echo=FALSE, message=FALSE,cache=TRUE}
library(dplyr)
data <- read.csv("assets/data/winequality-red.csv",sep=";")
data <- data %>% mutate(class=ifelse(quality <=4,"Low Quality",ifelse(quality>=8,"High Quality","Average")))
data$class <- factor(data$class, levels = c("Low Quality", "Average", "High Quality"), ordered=TRUE)
glimpse(data)

```

--- 
## How to Use the App

This Red Wine Quality data exploratory app demonstrates a core feature of Shiny: **interactivity** and **reactivity**. 

```{r echo=FALSE, message=FALSE,fig.width=14,fig.height=6}
library(ggplot2)
library(gridExtra)

winedata <- data 
g <- ggplot(winedata, aes(x = winedata[,1], y = ..density..)) +
    geom_histogram(position="identity",color = "blue",fill="white",binwidth = diff(range(winedata$fixed.acidity)) /30) +
    geom_density(color="magenta") +
    labs(x="fixed acidity", y = paste("Density of", "fixed acidity", sep =" "), 
         title = paste("Data Distribution for:","fixed acidity","(Bin size:",30,")")) +
    theme_bw() +
    theme(plot.title = element_text(face ="bold",color = "red", size = 16),
          axis.title = element_text(face ="bold",color = "blue", size = 12),
          axis.text = element_text(color = "blue", size = 10)
    ) 

    g1 <- ggplot(winedata, aes(x = class,y = fixed.acidity)) +
        geom_boxplot(aes(fill=class)) +
        geom_dotplot(binaxis = "y", binwidth = diff(range(winedata$fixed.acidity)) / 30 / 5, stackdir="center", fill = NA) +
        labs(x="", y = "fixed acidity", 
             title = paste("Boxplot for:","fixed acidity","by Wine Class")) +
        theme_bw() +
        theme(plot.title = element_text(face ="bold",color = "red", size = 16),
              axis.title = element_text(face ="bold",color = "blue", size = 12),
              axis.text = element_text(color = "blue", size = 10)
        ) 
    
    grid.arrange(g,g1,ncol=2)


```

--- 
## Let's try online

<iframe src="https://stevenwang.shinyapps.io/SWDDD/" width="800" height="320"></iframe>